% ─────────────────────────────────────────────────────────────────────────────
%  Sandu Stefan — CV
%  Template: moderncv (banking style)
%  Compile with: pdflatex or upload to Overleaf
% ─────────────────────────────────────────────────────────────────────────────
\documentclass[11pt, a4paper]{moderncv}

\moderncvstyle{banking}          % clean two-column header
\moderncvcolor{black}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scale=0.87]{geometry}
\usepackage{microtype}

% ── Personal data ─────────────────────────────────────────────────────────────
\name{Sandu}{Stefan}
\title{Economic Cybernetics Student}
\address{Bucharest}{Romania}
\phone[mobile]{+40 731 369 613}
\email{sandustefan2006@gmail.com}
\social[linkedin]{sandustefan}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}
\makecvtitle

% ── Professional Summary ──────────────────────────────────────────────────────
\section{Professional Summary}
Second-year Economic Cybernetics student at ASE Bucharest who builds full-stack AI
solutions under pressure. At VibeHack 2026 I reverse-engineered a live flight-search
API, integrated vision-capable LLMs, and shipped a WhatsApp-native AI assistant in
24 hours. I bridge quantitative thinking (Python, C++, statistics) with product-minded
design (Figma, Adobe CC) to turn ambiguous problems into working prototypes fast.
Actively seeking hackathons, research collaborations, and tech roles where impact is
measured in demos, not slides.

% ── Experience ───────────────────────────────────────────────────────────────
\section{Experience}

\cventry{Oct 2022 -- Nov 2022}{Social Media Marketing Assistant}{AdSymphony}{Bucharest}{}{
  \begin{itemize}
    \item Designed UX/UI prototypes for client websites using Figma, improving layout clarity and user flows.
    \item Created motion graphics and animated social media content in Adobe After Effects, boosting campaign engagement.
    \item Managed design file libraries and iterated on deliverables based on real-time client feedback.
  \end{itemize}
}

\cventry{Jun 2022 -- Aug 2022}{Retail Sales Assistant}{Emblema}{Bucharest}{}{
  \begin{itemize}
    \item Assisted customers with product selection and maintained a well-organised store floor, contributing to a positive shopping experience.
  \end{itemize}
}

% ── Education ────────────────────────────────────────────────────────────────
\section{Education}

\cventry{2024 -- 2027 (expected)}{B.Sc.\ Economic Cybernetics, Statistics \& Computer Science}%
        {Academy of Economic Studies (ASE)}{Bucharest}{}{
  Relevant coursework: Statistics, Mathematics, Econometrics, Databases, Programming Fundamentals.
}

% ── Skills ───────────────────────────────────────────────────────────────────
\section{Skills}

\cvitem{Design}{Adobe After Effects, Premiere Pro, Photoshop, Figma, Illustrator}
\cvitem{Programming}{C++, HTML, CSS, Python (learning)}
\cvitem{Productivity}{Microsoft Office (Excel, PowerPoint, Word), Google Analytics}
\cvitem{Languages}{Romanian (Native), English (Professional B2/C1), French (B1)}

% ── Projects \& Activities ───────────────────────────────────────────────────
\section{Projects \& Activities}

\cventry{14--15 Mar 2026}{Hackathon Participant -- Vola Travel AI Challenge}%
        {VibeHack Bucharest}{Bucharest}{}{
  Competed in a 24-hour AI hackathon sponsored by Vola.ro (Romania's largest online travel agency),
  challenged to build a WhatsApp-native AI travel assistant from scratch.
  \begin{itemize}
    \item Designed and prototyped a conversational AI agent integrating with WhatsApp (group and direct chats) to handle flight search, trip planning, and booking screenshot analysis.
    \item Reverse-engineered Vola.ro's live flight-search API and built a data integration layer for real-time price retrieval.
    \item Implemented image processing to identify travel destinations from photos and extract booking details from screenshots using vision-capable LLMs.
    \item Architected multi-turn conversation context management for group chat scenarios with multiple users and conflicting travel preferences.
  \end{itemize}
}

\cventry{Mar -- May 2022}{Volunteer Ambassador}{SCOALA-AMBASADOR -- EU Programme}{Bucharest}{}{
  Organised school activities supporting the EU School Ambassador initiative, promoting European values and civic engagement.
}

\cventry{Oct 2022}{Digital Skills Trainer}{Erasmus+ IDEAS Project}{Bucharest}{}{
  Welcomed and mentored visiting teachers and students from EU partner countries, delivering hands-on digital skills workshops.
}

\cventry{Apr 2023}{Competitor}{ASUS Learn \& Compete 2023}{Bucharest}{}{
  Competed in a national IT knowledge competition, demonstrating proficiency in computer science topics.
}

% ── Volunteer Work ───────────────────────────────────────────────────────────
\section{Volunteer Work}

\cventry{Sep 2021 -- May 2024}{Volunteer}{Neghi\c{t}\u{a} Children's Centre}{Bucharest}{}{
  Supported activities for underprivileged children over three years, demonstrating sustained commitment, empathy, and social responsibility.
}

\end{document}
